Java Based Memory Latency Simulator

### 2020-11-14 finalPaper/paper.tex
Finished removing filler content, so we can just drop our content in

\subsection{Running the Simulator}
\begin{itemize}
\item \textbf{Command Line}
  Either way that the simulator was compiled, the command
\begin{verbatim}
  java memSim
\end{verbatim}
  will start the simulator
\item \textbf{IDE}
  Given the multitude of IDEs that are available, please see your
  specific IDE's manual for how to compile and run the simulator.
\end{itemize}
Upon running the simulator, you will be prompted for a variety of 
simulator parameters. Each of these is crucial, and cannot be left blank.
\begin{verbatim}
How many Hard Drives would you like?
1
How many platters should each hard drive have?
4
And how big (in bytes) should each one be?
1024
How many RAM sticks would you like?
2
And how big (in bytes) should each one be?
128
Finally, how big (in bytes) would you like your CPU cache to be?
32
\end{verbatim}
After setting up the simulator, the components will each start up, and
you will be prompted to choose an option from the menu. You can choose to either
select based on the menu number, or the name.
\begin{verbatim}
Java Based Memory Latency Simulator
Developed by Pat Baumgardner, Adam Dachenhausen, Shah Syed
Supported commands:
move
read
write
help
exit
For help with a specific command type 'help [command]'
\end{verbatim}

\section{Explanation of Statistics Gathered}
\label{sec:expstats}

@@

\section{Disc}
\label{sec:disc}

@@

Summary, conclusions, discussion of the results, and ideas for future
work should be here.

Again, remember that writing is hard and writing well is very hard.  It
requires a long cycle of writing, reading, editing, rearranging,
rewriting, and so on.  If you are working in a group, have all group
members read and edit each others' sections.  Scientific writing
should be clear and concise.  If find a paragraph that says what can
be said in a sentence, cut it down to one sentence!

% it's nice to acknowledge any person or organization that helped out
% along the way.  The * after \section means this will not be assigned
% a section number
\section*{Acknowledgments}

The authors would like to thank all of our system administrators, past
and present, for installing the tools we needed on our systems and for
keeping those systems working smoothly while we completed this
project.

% Finally, the citations.  These lines tell latex what style to use
% (abbrv means to use first and middle initials instead of full names,
% among other things), and that your bibtex file is called
% references.bib
%
% bibtex alone should be enough to make anyone abandon any wysiwyg
% word processor and use latex for everything!
% 
% we'll also turn off double spacing for the citations
\singlespace
\bibliographystyle{abbrv}
\bibliography{references}

>>>>

\subsection{Running the Simulator}
\begin{itemize}
\item \textbf{Command Line}
  Either way that the simulator was compiled, the command
\begin{verbatim}
  java memSim
\end{verbatim}
  will start the simulator
\item \textbf{IDE}
  Given the multitude of IDEs that are available, please see your
  specific IDE's manual for how to compile and run the simulator.
\end{itemize}
Upon running the simulator, you will be prompted for a variety of 
simulator parameters. Each of these is crucial, and cannot be left blank.
{\singlespace
\begin{verbatim}
How many Hard Drives would you like?
1
How many platters should each hard drive have?
4
And how big (in bytes) should each one be?
1024
How many RAM sticks would you like?
2
And how big (in bytes) should each one be?
128
Finally, how big (in bytes) would you like your CPU cache to be?
32
\end{verbatim}
}
After setting up the simulator, the components will each start up, and
you will be prompted to choose an option from the menu. You can choose to either
select based on the menu number, or the name.
{\singlespace
\begin{verbatim}
Java Based Memory Latency Simulator
Developed by Pat Baumgardner, Adam Dachenhausen, Shah Syed
Supported commands:
move
read
write
help
exit
For help with a specific command type 'help [command]'
\end{verbatim}
}

\section{Explanation of Data Gathered}
\label{sec:expstats}

@@

\section{Discrepencies}
\label{sec:disc}

@@

Insert conclusions here.

\singlespace
\bibliographystyle{abbrv}
\bibliography{references}
